 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Customized the following:
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
% author:
% Trey Hunner (http://www.treyhunner.com/)
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	a4paper, % Uncomment for A4 paper size (default is US letter)
	12pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class


\title{Resume.PooriaAskariM}

%------------------------------------------------

\name{Pooria Askari Moqaddam} % Your name to appear at the top
\subtitle{Software Developer}  % Your subtitle description to appear at the top


\email{\href{mailto://pooriaaskarim@gmail.com}{pooriaaskarim@gmail.com}}
\phone{\href{tel://+989337330917} {+98 933 733 0917}}
\address{Shiraz, Iran}
\linkedin{\href{https://www.linkedin.com/in/pooriaaskarim/}{linkedin.com/in/pooriaaskarim/}}
\github{\href{https://github.com/pooriaaskarim}{github.com/pooriaaskarim}}

%----------------------------------------------------------------------------------------
\color{darkgray}
\begin{document}
\raggedright
\setlength{\headheight}{42pt} % Header Height
\setlength{\footskip}{10pt}  % Footer Skip


%----------------------------------------------------------------------------------------
%	Brief
%----------------------------------------------------------------------------------------

\begin{rSection}{Brief}
\bigskip
I am a Software Developer passionate about craftsmanship, dedicated to detail, and curious about DevOps practices and systems behavior and administration. I find complex technical/interpersonal challenges to be inevitable, yet exciting and rewarding aspects of software development.

With a decade of experience in different technical roles, I've been developing software solutions for the last 5 years using Flutter and Python, both independently and within collaborative teams.
I am eager to explore new opportunities, grow my expertise and experience.
\smallskip


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCES \& PROJECTS}
%------------------------------------------------
\bigskip
     \begin{rSubsection}{logd - Dart Log Daemon}{2025 - Present}{Open Source}{}
		\item \textbf{A modular logging service for Dart and Flutter applications.}
        \item \textbf{Hierarchical Loggers}: Dot-separated naming for inheritance (e.g., 'app.ui' inherits from 'app'), with dynamic propagation from parents or global.
        \item \textbf{Customizable Output}: Boxed, JSON, or custom formatters; console, file, network sinks; filters.
        \item \textbf{Stack Trace Integration}: Automatic caller extraction, configurable frame counts per level.
        \item \textbf{Timestamp Flexibility}: Timestamp formatters with timezone support.
        \item \textbf{Multi-line Buffers}: Atomic logging for complex messages.
        \item \textbf{Flutter/Dart Integration}: Attach to FlutterError and uncaught exceptions.
        \item \textbf{Available}  \href{https://pub.dev/packages/logd}{@pub.dev/logd}.
		\item \textbf{Open to contribution} \href{https://github.com/pooriaaskarim/logd}{@github/pooriaaskarim/logd}.  Licensed under \textbf{BSD 3-Clause}. 
        \\ \chip{Dart} \chip{logger} \chip{service}
	\end{rSubsection}
    
    \begin{rSubsection}{Flutter Notification Queue}{2025 - Present}{Open Source}{}
		\item \textbf{A overlay-based notification service for Flutter applications.} \textbf{Flutter Notification Queue} provides a comprehensive solution for displaying in-app notifications with advanced queuing, interactive gestures, multi-language support, and extensive customization options.\\
        Currently available for Android and Web. 
        \item Notification Channels are available to enable better management and styling of notification categories and sub-categories.
        \item Notification Queues are introduced as a way of positioning and controlling the behavior of notifications.
		\item \textbf{Open to contribution} \href{https://github.com/pooriaaskarim/flutter\_notification\_queue}{@github/pooriaaskarim/flutter\_notification\_queue}.  Licensed under \textbf{BSD 3-Clause}. 
        \\ \chip{Dart} \chip{Flutter} \chip{Notification} \chip{service}
	\end{rSubsection}
\bigskip
    \begin{rSubsection}{Rahandaaz} {2025 - Present}{Software Developer}{Shiraz, Iran}
		\item Collaborated with domain experts in developing Domain Linguistics and Domain Driven Design.
		\item Collaborated with a team of various roles in performance and UI/UX optimizations of the system.
        \\ \chip{Flutter}  \chip{GetX} \chip{Hive} \chip{Kotlin} \chip{DDD} \chip{Figma} \chip{Firebase} \chip{Agile/Scrum}
	\end{rSubsection}
\bigskip
	\begin{rSubsection}{Didehban Tejarat}{2023 - 2024}{Front-end Developer}{Shiraz, Iran}
		\item Collaborated with a team of different roles to develop a \textbf{CRM Application}.
		\item Designed and implemented \textbf{Software Architecture} and \textbf{CICD infrastructures} from scratch.
        \item Automated deployment using \textbf{Docker} and \textbf{Github Workflows}.
        \\ \chip{Flutter} \chip{GetX} \chip{Hive} \chip{OpenStreetMaps} \chip{Firebase} \chip{Docker}
	\end{rSubsection}
\bigskip
	\begin{rSubsection}{Chartix}{2022 - 2023}{Software Developer}{Shiraz, Iran}
        \item Designed and developed multi-platform \textbf{financial tools}, including a \textbf{Web Application} and a \textbf{Android App}, a \textbf{Telegram Bot}, and a \textbf{Caching and Logging system} to analyze the platform. 
        \item Enhanced application workflows by redesigning layers, resulting in better \textbf{performance} and improved \textbf{modularity} and \textbf{documentation}.
        \break \chip{Flutter} \chip{Python} \chip{BloC} \chip{Hive} \chip{Socket} \chip{Redis} \chip{TelegramAPI}
	\end{rSubsection}
\bigskip
	\begin{rSubsection}{FepCo}{2021 - 2022}{Junior Front-end Developer}{Shiraz, Iran}
	   	\item Practiced \textbf{Agile/Scrum methodology} in collaborative development of a modular \textbf{ERP-Software}.
        \item Developed proficiency in \textbf{Dart} and \textbf{Flutter}, \textbf{Design-Patterns}, \textbf{Clean-Code},  \textbf{Domain Driven Design}, \textbf{State Management}, \textbf{Route Management}, \textbf{Dependency Injection} and \textbf{translations}.
		\item Collaborated in \textbf{UI/UX design} flows.
        \break \chip{Flutter} \chip{GetX} \chip{Clean Code} \chip{DDD} \chip{Scrum}
	\end{rSubsection}
\bigskip
    \begin{rSubsection}{Diakoo}{2018 - 2019}{System Administrator}{Shiraz, Iran}
		\item Set-up and maintenance of Linux/Windows servers to host Java-based systems.
        \item Set-up and maintenance of VoIP servers.
        \item Collaborated with developers in designing a secure Video Streaming service with limited access and download protection.
	\end{rSubsection}
\bigskip
    \begin{rSubsection}{Various Positions}{2014 - 2019}{Computer Hardware/Software Technician}{Shiraz, Iran}
		\item Computer Systems repair and maintenance.
        \item Computer Networks (Passive/Active) configurations and maintenance.
        \item Linux Server Administrations and Automations.
	\end{rSubsection}
%------------------------------------------------
\bigskip
\end{rSection}


%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
    \bigskip
	\begin{tabular}{@{} >{\bfseries}l @{\hspace{8pt}} l @{}}
    \bigskip Technologies &
                \smallskip \bigChip{Dart}\bigChip{Python}\bigChip{Kotlin}\bigChip{Docker}\bigChip{Linux-based Systems} \\
            
            Tools &
    \smallskip  \bigChip{Flutter}\bigChip{BloC-Pattern}\bigChip{GetX}\bigChip{RxDart}
                 \bigChip{Provider-Pattern}  \\
    \smallskip    &  \bigChip{Firebase APIs}\bigChip{OpenStreetMaps API}\bigChip{Google Console APIs} \\
    \bigskip    &  \bigChip{Android Studio}\bigChip{Vim}\bigChip{PyCharm}\bigChip{Git}\bigChip{Azure}\bigChip{Figma} \\   

            Industrial Knowledge &
    \smallskip  \bigChip{Domain Driven Design}\bigChip{Software Architecture}\bigChip{Design Patterns} \\
		          
    \bigskip    &  \bigChip{Clean Code}\bigChip{SOLID}\bigChip{OOP}\bigChip{Agile Scrum Methodology}\bigChip{CICD} \\
            Databases &
                \bigChip{Hive}\bigChip{Isar}\bigChip{Redis}\bigChip{mySql} \\
	\end{tabular}
    \bigskip
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
	\bigskip
	\textbf{Islamic Azad University} \hfill \textit{2018} \\ 
	Bachelor’s Degree in Computer Software Technology \& Engineering \\
	\bigskip
    \textbf{Arak University of Technology} \hfill \textit{2015} \\ 
	Undergraduate Degree Electrical Power Transmission / Installation
\end{rSection}


\end{document}
